The problem and promise of scale in animal social multilayer networks

### 2020-02-09 paper/manuscript.Rmd
Update manuscript.Rmd

Animal movement undoubtedly affects an individual's social environment
[@Strandburg-Peshkin_2015]. Movement is a dynamic process that is related
to the resources an individual consumes within their home range and the space
that they use (Van Moorter et al. 2016). Collective movement can reduce
group-level predation via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
(Jolles et al. 2019). Social processes, movement decisions, and space use are
inextricably linked and multilayer networks represent a potential analytical
framework for linking these processes (e.g. Mourier et al. 2019).

>>>>

Social processes, movement decisions, and space use are inextricably linked 
and multilayer networks represent a potential analytical framework for linking 
these processes (e.g. Mourier et al. 2019). Movement as a collective group can 
reduce per capita predation risk via detection-dilution trade-offs and improve 
information transfer about the quality or location of resources to other group 
members (Jolles et al. 2019). In our case study, we integrate proximity based 
social networks that inherently rely on animal collective movement and, in general, 
we found that movement is likely an important mechanism driving social network 
connectivity within and between habitat types.
